Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-21 R0V0.tex
Start to change the example
Waiting for quality check of sets \mathscr{K} and \Xi
change header
Change abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Master	 													   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem under consideration is the design of structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, the search for these functions is non-convex \cite{Rantzer:2001}. On the other hand, control-contraction metrics can provide controllers through a convex optimization problem. The drawback is that it may require the a function with $n^2$ elements. By exploiting sparsity, this number of verification can be decreased and the convex optimization problem can also be distributed. An example illustrates the approach for a network system.
\end{abstract}

@@

@@

In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix). The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Manchester20161020											   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem is the design of structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, numerical methods employed to construct for these functions usually leads to a non-convex optimization problem. Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements. In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable topological (distributed) structures. By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program. An example illustrates the approach for a network system.
\end{abstract}

@@

\todo[inline]{Waiting for quality check of the definition of the sets $\mathscr{K}$ and $\Xi$.}

@@

In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and for each $i$ $\mathbf{X}(\mathscr{K}(k))=\{x\}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}
